---
title: "Module 12"
author: "Joaquin Monque"
date: "`r Sys.Date()`"
output: html_document
---

# SimpleSurveyAnalysis Package

## Introduction

The SimpleSurveyAnalysis package is designed to simplify the process of analyzing survey data. It offers a set of straightforward tools for social science students and researchers to summarize, visualize, and clean survey results.

### Installation

```{r}
# Install SimpleSurveyAnalysis from CRAN
# install.packages("SimpleSurveyAnalysis")
```

------------------------------------------------------------------------

## Main Functions

### Descriptive Statistics

**`'describeSurvey()'`**

Calculates descriptive statistics for quantitative survey questions.

-   **Purpose**: Provide summary statistics including mean, median, mode, range, variance, and standard deviation.

-   **Inputs**:

    -   **`'data'`**: A data frame containing survey data.

    -   **`'variables'`**: Vector of column names in **`'data'`** for which descriptive statistics are calculated.

-   **Outputs**: A data frame with descriptive statistics for each specified variable.

**Example**

```{r}
# describeSurvey(data = survey_data, variables = c("age","income"))
```

------------------------------------------------------------------------

### Frequency Analysis

**`'frequencyCount()'`**

Generates frequency counts and percentages for categorical survey responses.

-   **Purpose:** Offer a clear view of how respondents have answered categorical questions, supporting multiple-choice formats.

-   **Inputs**:

    -   **'`data`'** : A data frame containing survey data.

    -   **'`question`'** : The column name in data representing the categorical question to analyze.

-   **Outputs**: A data frame showing each response option, its frequency count, and percentage of total responses.

**Example**

```{r}
# frequencyCount(data = survey_data, question = "satisfaction_level")
```

------------------------------------------------------------------------

### Visualization Tools

**`'plotSurvey()'`**

Creates basic visualizations for survey data, including bar charts, pie charts, and histograms.

-   **Purpose**: Aid in the interpretation and presentation of survey results through visual means.

-   **Inputs**:

    -   **`'data'`**: A data frame containing survey data.

    -   **`'question'`**: The column name in **`'data'`** to visualize.

    -   **`'type'`**: The type of visualization ("bar", "pie", or "histogram").

-   **Outputs**: A plot object displaying the chosen visualization.

**Example**

```{r}
# plotSurvey(data = survey_data, question = "satisfaction_level", type = "bar")
```

------------------------------------------------------------------------

### Data Cleaning

**`'cleanSurveyData()'`**

Preprocesses and cleans survey data, handling missing values and inconsistent response categories.

-   **Purpose**: Ensure survey data is clean and consistent before analysis.

-   **Inputs**:

    -   **`'data'`**: A data frame containing survey data.

    -   **`'options'`**: A list of options for handling missing data and recoding responses.

-   **Outputs**: A data frame with cleaned and preprocessed data.

**Example**

```{r}
# cleanSurveyData(data = survey_data, options = list(missing = "exclude", recode = TRUE))
```

------------------------------------------------------------------------
